### 2019-02-19 sections/conclusions.tex
match conclusion with contributions

\fixme{moet passen bij de contributions}
In this paper we have developed a domain-specific calculus for declarative interactive workflows, named \TOPHAT.
We have shown that our calculus is modular, and clearly seperated from the host language it is embedded in.
By developing this calculus, we have identified the essence of Task-Oriented Programming.
In addition to the formal semantics, we have also demonstrated how to build a user interface from a task description.
We have compared \TOPHAT with workflow moddeling languages, process algebras, functional reactive programming and session types to point out differences and similarities.
Finally, we have proven type safety and progress for our language.

>>>>

In this paper we have identified and intuitively described the essence of task-oriented programming.
We then formalized this essence by developing a domain-specific calculus for declarative interactive workflows, called \TOPHAT.
The task calculus and the host language are clearly separated, to make explicit where the boundaries are.
The semantics of the task layer is driven by user input.
We have compared \TOPHAT with workflow moddeling languages, process algebras, functional reactive programming and session types to point out differences and similarities.
Finally, we have proven type safety and progress for our language.
